An agent-based model of interdisciplinary interactions in science

### 2020-05-25 Docs/Papers/ABMInterdisc/paper/paper.tex
template

\input{WPHeader.tex}

\title{An agent-based model of interdisciplinary interactions in science\\%\medskip
%\textit{Ecole thématique de Rochebrune 2018\\
%Proposition de Communication
}
}
\author{\noun{Juste Raimbault}$^{1,2}$\\
$^{1}$ UMR CNRS 8504 Géographie-cités\\
$^{2}$ UMR-T IFSTTAR 9403 LVMT
}
\date{}

@@

\justify

\begin{abstract}
An increased interdisciplinarity in science projects has been highlighted as crucial to tackle complex real-world challenges, but also as beneficial for the development of disciplines themselves. This paper introduces a parcimonious agent-based model of interdisciplinary relationships in collective entreprises of knowledge discovery, to investigate the impact of scientist-level decisions and preferences on global interdisciplinarity patterns. Under the assumption of simple rules for individual researcher project management, such as trade-offs between invested time overhead and knowledge benefit, model simulations show that individual choices influence the distribution of compromise points between emergent level of disciplinary depth and interdisciplinarity in a non-linear way. Different structures for collaboration networks also yield various outcomes in terms of global interdisciplinarity. We conclude that independently of the research field, the organization of research, and more particularly the local balancing between vertical and horizontal research, already influences the final positioning of research results and the extent of the knowledge front. This suggests direct applications to research policies with a bottom-up leverage on the interactions between disciplines.
\end{abstract}

@@

https://journals.plos.org/plosone/article/citation?id=10.1371/journal.pone.0221907 : assymetry of interdisc

https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.3000065

importance of teams vs solo authors Pavlidis, I., Petersen, A. M., \& Semendeferi, I. (2014). Together we stand. Nature Physics, 10(10), 700.

https://www.nature.com/articles/s41467-019-11401-8

VANVLOKHOVEN2019751 : model for oa and research quality

@@

Akerlof, G. A., \& Michaillat, P. (2018). Persistence of false paradigms in low-power sciences. Proceedings of the National Academy of Sciences, 201816454.

\subsection*{Perspectivism and Model Coupling}

@@

We postulate that this approach to science may be a powerful tool to foster interdisciplinary collaborations, if used in a reflexive way in the construction of projects. More precisely, an ``Applied Perspectivism'' would imply a high-level of reflexivity for each agent implied, a mapping of the different layers of the enterprise and the positioning of each agent regarding the domains of knowledge. This way, in the particular case of model coupling, the explicitation of positioning and of the structure of each knowledge implied should ease interactions. As Banos points out~\cite{banos2013pour}, transversal work must alternate with deeper investigations in each discipline, in a kind of ``virtuous circle''. This raises the issue of, before individual researcher particularities, how a given collective structure of scientific knowledge production should balance between these two. It is clear that this question is deeply endogenous to each studied subject, and even each particular approach taken, but within the applied knowledge framework described above, we have reasons to believe that certain structural properties may be rather general. Indeed, each discipline is expected to bring components for each knowledge domain, and the co-evolving perspective is built on their interrelations. We propose to investigate here basic aspects of this issue, with means of agent-based modeling.

@@

\subsection*{An agent-based Model of Interdisciplinarity}

@@

http://bingweb.binghamton.edu/~sayama/NSF-SoO/ abm for group orga

Pluchino, A., Biondo, A. E., \& Rapisarda, A. (2018). Talent Versus Luck: The Role Of Randomness In Success And Failure. Advances in Complex Systems, 21(03n04), 1850014.

Twin-Win Model: A human-centered approach to research success

Modeling research universities: Predicting probable futures of public vs. private and large vs. small research universities

\paragraph{Model}

@@

\paragraph{Results}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.32\linewidth]{figures/depth-sigma_alpha0-5_rho0}
	\includegraphics[width=0.32\linewidth]{figures/interdisc-sigma_alpha0-5_rho0}
	\includegraphics[width=0.32\linewidth]{figures/pareto_alpha0-5_rho0}
	\caption{\textbf{Patterns of interdisciplinarity from model simulations.} We show measures of depth and interdisciplinarity (left and middle) at fixed $\alpha=0.5$ and network structure, for varying discrete choice parameter $\beta$ as a function of individual extent $\sigma$. On the right, the Pareto front of average point between these two objectives.}
	\label{fig:plots}
\end{figure*}

\paragraph{Possible extensions}

@@

%%%%%%%%%%%%%%%%%%%%
%% Biblio
%%%%%%%%%%%%%%%%%%%%
\footnotesize

\bibliographystyle{apalike}
\bibliography{/Users/Juste/ComplexSystems/CityNetwork/Biblio/Bibtex/CityNetwork,biblio}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.   
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

%\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}

\linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Raimbault} %use et al only if is more than 1 author
\def\Authors{Juste Raimbault\,$^{1,2,3,*}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Center for Advanced Spatial Analysis, University College London, London, United Kingdom\\
$^{2}$UPS CNRS 3611 ISC-PIF, CNRS, Paris, France\\
$^{3}$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{CASA, UCL, 90 Tottenham Court Road, London W1T 4TJ, United Kingdom}

\def\corrEmail{juste.raimbault@polytechnique.edu}

\begin{document}
\onecolumn
\firstpage{1}

\title[Agent-based modeling interdisciplinarity]{An agent-based model of interdisciplinary interactions in science}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

@@

\begin{abstract}

%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
%\section{}
An increased interdisciplinarity in science projects has been highlighted as crucial to tackle complex real-world challenges, but also as beneficial for the development of disciplines themselves. This paper introduces a parcimonious agent-based model of interdisciplinary relationships in collective entreprises of knowledge discovery, to investigate the impact of scientist-level decisions and preferences on global interdisciplinarity patterns. Under the assumption of simple rules for individual researcher project management, such as trade-offs between invested time overhead and knowledge benefit, model simulations show that individual choices influence the distribution of compromise points between emergent level of disciplinary depth and interdisciplinarity in a non-linear way. Different structures for collaboration networks also yield various outcomes in terms of global interdisciplinarity. We conclude that independently of the research field, the organization of research, and more particularly the local balancing between vertical and horizontal research, already influences the final positioning of research results and the extent of the knowledge front. This suggests direct applications to research policies with a bottom-up leverage on the interactions between disciplines.

\tiny
 \keyFont{ \section{Keywords:}} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

\section{Introduction}

@@

\cite{101371journalpone0221907} assymetry of interdisc between social and hard sciences in the credit given to other disciplines

\cite{10.1371/journal.pbio.3000065} competition for funding is inefficient

\cite{pavlidis2014together} importance of teams vs solo authors

\cite{zeng2019increasing} individual interdisciplinarity: in time, more scientists switch between topics

\cite{VANVLOKHOVEN2019751} : model for oa and research quality

@@

\cite{akerlof2018persistence} paradigms persist in ``low-power'' sciences

\subsection{Perspectivism and Model Coupling}

@@

We postulate that this approach to science may be a powerful tool to foster interdisciplinary collaborations, if used in a reflexive way in the construction of projects. More precisely, an ``Applied Perspectivism'' would imply a high-level of reflexivity for each agent implied, a mapping of the different layers of the enterprise and the positioning of each agent regarding the domains of knowledge. This way, in the particular case of model coupling, the explicitation of positioning and of the structure of each knowledge implied should ease interactions. As Banos points out~\cite{banos2013pour}, transversal work must alternate with deeper investigations in each discipline, in a kind of ``virtuous circle''. \cite{banos2017knowledge}
synergy more than interdisciplinarity in itself \cite{leydesdorff2020measurement}
This raises the issue of, before individual researcher particularities, how a given collective structure of scientific knowledge production should balance between these two. It is clear that this question is deeply endogenous to each studied subject, and even each particular approach taken, but within the applied knowledge framework described above, we have reasons to believe that certain structural properties may be rather general. Indeed, each discipline is expected to bring components for each knowledge domain, and the co-evolving perspective is built on their interrelations. We propose to investigate here basic aspects of this issue, with means of agent-based modeling.

@@

\subsection{Contribution}

@@

%http://bingweb.binghamton.edu/~sayama/NSF-SoO/
\cite{dionne2019diversity} abm for group orga

\cite{pluchino2018talent} role of randomness in individual trajectories success

\cite{shneiderman2018twin} model for research success

\cite{rouse2018modeling} research organization: public-private, small-large

\section{An agent-based Model of Interdisciplinarity}

@@

\section{Results}

@@

\section{Discussion}

\subsection{Possible extensions}

@@

\section*{Conflict of Interest Statement}
%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}

JR designed the study, coded the model, conducted the experiments, and wrote the paper.

\section*{Funding}

\section*{Acknowledgments}

%\section*{Supplemental Data}

\section*{Data Availability Statement}

%The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK].

%\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{biblio.bib}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

\section*{Figure captions}

%%% Please be aware that for original research articles we only permit a combined number of 15 figures and tables, one figure with multiple subfigures will count as only one figure.
%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.eps and logos.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png
%%%  NB logo1.eps is required in the path in order to correctly compile front page header %%%

%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=10cm]{logo1}% This is a *.eps file
%\end{center}
%\caption{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
%\end{figure}

%
%\begin{figure*}
%	\centering
%	\includegraphics[width=0.32\linewidth]{figures/depth-sigma_alpha0-5_rho0}
%	\includegraphics[width=0.32\linewidth]{figures/interdisc-sigma_alpha0-5_rho0}
%	\includegraphics[width=0.32\linewidth]{figures/pareto_alpha0-5_rho0}
%	\caption{\textbf{Patterns of interdisciplinarity from model simulations.} We show measures of depth and interdisciplinarity (left and middle) at fixed $\alpha=0.5$ and network structure, for varying discrete choice parameter $\beta$ as a function of individual extent $\sigma$. On the right, the Pareto front of average point between these two objectives.}
%	\label{fig:plots}
%\end{figure*}
%
